Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-07-01 reports/paper1/paper.tex
Revise paper, add getTime for AllNull

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test sample with purposely designed voids. An x-ray projection was obtained and compared with the simulated projection from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$. The Benjamini-Hochberg (BH) \citep{benjamini1995controlling} procedure was used to select the threshold such that the false discovery rate (FDR) is less than 5\%. The FDR is defined as
\begin{equation}
\text{FDR}=\expectation\left[\dfrac{\text{number of false positives}}{\text{number of positives}}\right]
\end{equation}
where the ratio is defined to be zero when the number of positives is zero. It indicates the average proportion of positives which are false. The BH procedure is done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
\begin{equation}
  \alpha = \frac{0.05 k}{N}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
  \ .
\end{equation}

@@

The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}. The running times are compared with the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation. Compared to the mean-variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.

@@

For good results, the faces of the AM sample were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.

@@

\section{Appendix}
Code which reproduces this paper can be found on the \emph{GitHub} page.

\section{Acknowledgements}
This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme).

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean-variance null filter}
      \end{subfigure}
    }
  \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image. The mean-variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plots summarise the 100 repeated measurements of the running times.}
  \label{fig:inference_timing}
\end{figure}

>>>>

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test sample with purposely designed voids to see if they can be detected. The methods section is split into four parts. In Section \ref{subsection:appratus}, a CAD model of the test sample was designed and manufactured using AM. Replicate x-ray projections were obtained of the test sample as well as a simulated projection, without the voids, using \emph{aRTist}. Section \ref{subsection:empiricalnullfilter} explains how the obtained and simulated projections were compared to detect these voids under the face of uncertainty. The uncertainty was modelled using the replicated projections. To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The implementation of the empirical null filter is discussed in Section \ref{subsection:computational} and tested on small simulated projections in Section \ref{subsection:simulation}. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$. It controls the per comparison error rate (PCER) \citep{benjamini1995controlling} which is the average proportion of false positives out of all tests or
\begin{equation}
\text{PCER}=\dfrac{1}{N}\expectation\left[\text{number of false positives}\right]
\end{equation}
where $N$ is the number of pixels to test. A typical choice is $\alpha=0.05$ \citep{wasserstein2019moving}. This method of thresholding is flawed because of the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. For example, suppose none of the pixels represents a defect, then on average, 5\% of these pixels are tested positive and falsely so. This is troublesome and costly because false positives suggest a defect in areas where there are not any defects.

The false discovery rate (FDR) is the average proportion of positives which are false or
\begin{equation}
\text{FDR}=\expectation\left[\dfrac{\text{number of false positives}}{\text{number of positives}}\right]
\end{equation}
where the ratio is defined to be zero when the number of positives is zero. The Benjamini-Hochberg (BH) \citep{benjamini1995controlling} procedure was used to select the threshold such that the FDR is less than 5\%. This allows control for false positives relative to the number of positives. The BH procedure is done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$ and then using the threshold
\begin{equation}
  \alpha = \frac{0.05 k}{N}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
  \ .
\end{equation}

@@

The running times for the empirical null filter with radius \SI{50}{\pixel} were measured to be \SI[separate-uncertainty = true]{26.72(35)}{\second}. This was compared to simpler filters such as the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation. Running times of \SI[separate-uncertainty = true]{0.0100(12)}{\second} were achieved using the mean-variance filter. With both of these filters, running time increased with kernel radius.

@@

For good results, the faces of the test sample were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM products with complicated geometry and curved surfaces.

@@

\section{Appendix}
Code which reproduces this paper can be found on the \emph{GitHub} page \url{https://github.com/shermanip/oxwasp_insideout}.

\section{Acknowledgements}
This work is funded by EPSRC grant numbers EP/K031066/1 (Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing) and EP/L016710/1 (EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme). We would like to thank Wilfred S.~Kendall for his role as principal investigator.

@@
